\documentclass[transmag]{IEEEtran}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amsfonts,amssymb,amsmath}
\usepackage{hyperref}
\usepackage{minted}
\usepackage{pdflscape}
\usepackage[justification=centering]{caption}
\usepackage{float}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={Overleaf Example},
    pdfpagemode=FullScreen,
    }

\usepackage{graphicx}
\usepackage{tabulary}
\usepackage{listings}


\usepackage[utf8]{inputenc}

\usepackage{xcolor}

\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}


\lstdefinelanguage{JavaScript}{
  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
  keywordstyle=\color{blue}\bfseries,
  ndkeywords={class, export, boolean, throw, implements, import, this},
  ndkeywordstyle=\color{darkgray}\bfseries,
  identifierstyle=\color{black},
  sensitive=false,
  comment=[l]{//},
  morecomment=[s]{/*}{*/},
  commentstyle=\color{purple}\ttfamily,
  stringstyle=\color{red}\ttfamily,
  morestring=[b]',
  morestring=[b]",
}

\lstset{
   language=JavaScript,
   backgroundcolor=\color{white},
   extendedchars=true,
   basicstyle=\footnotesize\ttfamily,
   showstringspaces=false,
   showspaces=false,
   tabsize=2,
   breaklines=true,
   showtabs=false,
   captionpos=b
}


% \lstdefinestyle{mystyle}{
%     backgroundcolor=\color{backcolour},   
%     commentstyle=\color{codegreen},
%     keywordstyle=\color{magenta},
%     numberstyle=\tiny\color{codegray},
%     stringstyle=\color{codepurple},
%     basicstyle=\ttfamily\footnotesize,
%     breakatwhitespace=false,         
%     breaklines=true,                 
%     captionpos=b,                    
%     keepspaces=true,                 
%     numbers=left,                    
%     numbersep=5pt,                  
%     showspaces=false,                
%     showstringspaces=false,
%     showtabs=false,                  
%     tabsize=2
% }

% \lstset{style=mystyle}


\usepackage[linesnumbered,ruled,vlined]{algorithm2e}
\hypersetup{
    linkcolor=blue,
    anchorcolor=blue,
    citecolor=black,
    filecolor=blue,
    menucolor=blue,
    runcolor=blue,
    }

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\markboth{COMP90024 Team 39}
{$>$ REPLACE THIS LINE WITH YOUR PAPER IDENTIFICATION NUMBER $<$}
\begin{document}

\title{Twitterlance: Fitness Analysis for Australia}

\author{Zihao Yang 1252410, Yuqi Zhang 777603, Xin Li 1029029\\
Wei Li 956833, Zihao Hu 977716}


\IEEEtitleabstractindextext{\begin{abstract}A highly scalable distributed system is developed and deployed on Melbourne Research Cloud to collect and analyse big data from Twitter. The entire deployment process is handled by Ansible tasks to enable automation and scalability. All software services are built into Docker container images for painless deployment, while the containers run in a Docker Swarm for the simplicity of scaling. The most vibrant city, sports preferences of each city, and the sport enthusiasts across six cities in Australia are identified from over 10 million tweets and the data collected from AURIN, Twitter and ESPN. The core web application, harvester, and controllers are wrapped in Django, which runs as a scalable cluster that supports parallel data collection for a better performance. All data is stored in CouchDB and processed by MapReduce in batch jobs. Spark runs as a complement to CouchDB due to the limitation of custom reduce functions on partitioned CouchDB database. Three scenarios are covered at data analysis phase, where the shows that Canberra is the most vibrant city, while running, footy, and walking are the most popular sports. Top five sports enthusiasts are identified in a rank. \end{abstract}

% 1) twitter harvest
% 2) couchdb save our data
% 3) spark couchdb Django analysis
% 4) frontend display the result
% 5) MRC docker dockerswarm HAPproxy

\begin{IEEEkeywords}
Twitterlance, Sport, Data Analysis, Scalability, Automation, Cloud, Cluster, AURIN, Twitter
\end{IEEEkeywords}}

\maketitle

\input{Context/intro}

\input{Context/background_related}

\input{Context/software_dev}

\input{Context/architecture}

\input{Context/data_analysis}

\input{Context/conclusion}

\input{Context/appendix}

\newpage


\bibliographystyle{IEEEtran}
\bibliography{ref}

\end{document}
